%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref} % For \href command

\name{Andrew Kim} % Your name
\address{
(630)~$\cdot$~945~$\cdot$~6470 ~$\diamond$~
\href{mailto:akim9165@gmail.com}{akim9165@gmail.com} ~$\diamond$~
\href{https://linkedin.com/in/anndrewkimm}{linkedin.com/in/anndrewkimm} ~$\diamond$~
\href{https://github.com/anndrewkimm}{github.com/anndrewkimm} ~$\diamond$
}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\textbf{California State University, Fullerton} \hfill {Expected December 2026} \\
\textmd{B.S. in Computer Science, Minor in Math} \smallskip \\
\textmd{Overall GPA: 3.60} \smallskip \\
\textmd{\textbf{Relevant Coursework:} Data Structures \& Algorithms, Artificial Intelligence, Probability Theory, Statistics, Linear Algebra}


\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\begin{rSection}{TECHNOLOGIES}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages: \textmd{C++, Python, Java, JavaScript, SQL, Swift, HTML, CSS} \\%
Frameworks \& Libraries: \textmd{Pytorch, Scikit-learn, React, Node.js, Express.js, Tailwind CSS, Numpy,} \\
\textmd{XGBoost, Pandas}\\
Tools \& Platforms: \textmd{Microsoft Copilot Studio, Power Automate, Jira, Freshservice, Databricks}\\
\textmd{Postman, Firebase, Git, GitHub, REST APIs, JSON} \\

\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Flexera}{May 2026 - August 2026}{Data Analytics Intern}{Itasca, IL}
\item \textmd{Designed and developed an AI-powered ticket management assistant using \textbf{Microsoft Copilot Studio}, enabling natural-language querying, filtering, and reporting across \textbf{Jira} and \textbf{Freshservice} data.}

\item \textmd{Built \textbf{Power Automate} workflows and \textbf{REST API} integrations to retrieve, transform, and aggregate enterprise ticket data from multiple platforms.}

\item \textmd{Implemented automated pagination, dynamic query generation, and \textbf{JSON processing pipelines} to support large-scale ticket retrieval and analytics.}

\item \textmd{Developed precomputed aggregation pipelines for metrics including ticket volume, status distribution, assignee workload, and SLA reporting to improve response speed and accuracy.}
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECT SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\begin{rSubsection}{Game Outcome Prediction Platform}{June 2025 - August 2025}{}{}
\item \textmd{Built and deployed a multi-class \textbf{XGBoost machine learning system} to predict player outcomes, achieving \textbf{90\% accuracy} for win/loss classification and \textbf{50\% accuracy} for 8-class placement prediction.}
\item \textmd{Designed a \textbf{data pipeline} using the Riot Games API to collect, clean, and aggregate large-scale match statistics for model training.}
\item \textmd{Applied \textbf{cross-validation and feature engineering} to improve model robustness and generalization.}
\item \textmd{Developed a \textbf{Node.js REST API} to serve real-time prediction requests and integrated a React frontend for visualization and user interaction.}
\end{rSubsection}

\begin{rSubsection}{Real-Time Multiplayer Game with Firebase Integration}{August 2024 - September 2024}{}{}
\item \textmd{Developed a real-time 2D web application supporting concurrent players with synchronized state updates.}
\item \textmd{Integrated Firebase cloud services for \textbf{real-time data synchronization} and multi-user interaction.}
\item \textmd{Implemented responsive user input handling and cloud-hosted media assets.}
\end{rSubsection}

\end{rSection}

%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
